Corpus Stats

### 2019-03-19 notebooks/corpus_stats_and_plots.Rmd
fixed small error in c locs and worked more on notebook

r_c_df <- data.frame(package_name = names(r_counts), loc_r = r_counts)
# looks weird sorted
# r_c_df <- r_c_df[order(r_c_df$loc_r),]

plot_r_counts <- ggplot( data=r_c_df, aes(x=1:length(r_counts), y=loc_r, group=1))
plot_r_counts <- plot_r_counts + geom_line() + geom_point()
plot_r_counts <- plot_r_counts + labs(x = "Corpus of Analyzed Packages", y = "Lines of R Code in Package")

@@

>>>>

r_c_df <- data.frame(package_name = names(r_counts), loc_r = r_counts)
# looks weird sorted
r_c_df <- r_c_df[order(r_c_df$loc_r),]
# looks weirder log10-scaled
r_c_df$loc_r <- log10(r_c_df$loc_r)

plot_r_counts <- ggplot( data=r_c_df, aes(x=1:length(r_counts), y=loc_r, group=1))
plot_r_counts <- plot_r_counts + geom_line() + geom_point()
plot_r_counts <- plot_r_counts + labs(
  title = "Analysis of R Corpus (R Code Portion)",
  x = "Corpus of Analyzed Packages", 
  y = "Lines of R Code in Package (Log10-scaled)"
)

@@

The outlier is the spatstat package.
How about for C?

c_c_df <- data.frame(package_name = names(c_counts), loc_c = c_counts)
# removing packages w/ no C code (-1)
c_c_df$loc_c <- lapply(c_c_df$loc_c, function(loc) if (loc == -1) 0 else loc)
# looks weird sorted
c_c_df <- c_c_df[order(c_c_df$loc_c),]
# looks weirder log10-scaled
c_c_df$loc_c <- log10(c_c_df$loc_c)

plot_c_counts <- ggplot( data=c_c_df, aes(x=1:length(c_counts), y=loc_c, group=1))
plot_c_counts <- plot_c_counts + geom_line() + geom_point()
plot_c_counts <- plot_c_counts + labs(
  title = "Analysis of R Corpus (C Code Portion)",
  x = "Corpus of Analyzed Packages", 
  y = "Lines of C Code in Package (Log10-scaled)"
)

plot_c_counts <- plot_c_counts + theme(axis.text.x = element_blank())

# plot it
plot_c_counts
